---
title: "Course Project 1"
author: "Joseph Audras and Devin Romines"
date: "April 12, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

# Introduction
dataset source: https://www.kaggle.com/lava18/google-play-store-apps

# Description

The Google Play Store Data Set is a data set containing data on over 10,000 apps in the Google Play Store for Android products.  The data set looks at things such as rating, number of installations, and genre to produce a plethora of information on each app.  In addition to this data set, we are also looking at the google Play Store User Review Data Set, which contains the actual content on approximately 65,000 user reviews of apps.  Additional data for this set contains some Sentiment Analysis values for the perceived mood of a particular review.

The data sets were gathered from https://www.kaggle.com/lava18/google-play-store-apps which was last updated 2 months ago, giving us Version 6 which we are working with.  The data was posted by Lavanya Gupta, a software engineer at HSBC Software Development in India.  More information on her can be found here https://www.kaggle.com/lava18.  The information in the data set was scraped from the Google Play Store by Lavanya Gupta, in an effort to provide similar information on its apps as is publically available from the Apple App Store so that developers may be more inclined to work in the Android market.


```{r}
df <- read.csv("googleplaystore.csv")
dfReviews <- read.csv("googleplaystore_user_reviews.csv")
```

```{r}
library(tidyverse)
library(lubridate)
```

# Data dictionary

# App list

App – Factor, 9660 levels – The name of the app.

Category – Factor, 34 levels – The general type of app, such as Dating, Cooking, or Art and Design

Rating – Numerical, range from 0-5 – The rating of the app on a scale from 0-5.

Reviews – Factor, 6002 levels – The number of reviews that the app received.

Size – Factor, 462 levels – The size in megabytes of the app.

Installs – Factor, 22 levels – The number of installations an app received, given in terms of 0+ 1,000,000,000+

Type – Factor, 4 levels – Whether or not the app is free.

Price – Factor, 93 levels – The Price of the app given as a factor.

Content.Rating – Factor, 7 levels – The rating for the app, E for Everyone, Adults only 18+, etc.

Genres – Factor, 120 levels – The genre of the app, Action, Action and Adventure, etc.

Last.Updated – Factor, 1378 levels – The date on which the app was last updated, given in multiple formats.

Current.Ver – Factor, 2834 levels – The current version of the app, 0.0.0.2, 0.0.1, etc.

Android.Ver – Factor, 35 levels – The version of Android phone required to use the app, given in the form, “version and up”


# App review vars - dfReviews

App – Factor, 1074 levels – The name of the app.

Translated_Review – Factor, 27995 levels – The actual, unedited text of the user reviews, containing many grammatical and spelling errors.

Sentiment – Factor, 4 levels – The self-reported mood the user associated with the particular app, positive, negative, etc.

Sentiment_Polarity – Numerical, range from -1 to +1.  The Sentiment Polarity value as calculated from Sentiment Analysis, based on the Sentiment variable.  More information can be found at this link https://en.wikipedia.org/wiki/Sentiment_analysis.

Sentiment_Subjectivity – Numerical, range from -1 to +1.  The Sentiment Subjectivity value as calculated from Sentiment Analysis, based on the Sentiment variable.  More information can be found at this link https://en.wikipedia.org/wiki/Sentiment_analysis.



# Data Cleaning

# App df:

```{r}

# App: there are some broken characters from other languages, ignore and exlude rows

# Cateogry: no changes

# rating: some ratings have a NaN, exlude those rows with those values

# reviews: cast to num

# size: remove any "varies with device" rows
# convert k, M, B to numbers and to appropriate nums and cast after

# installs: remove + and ,
# cast to num

# type: remove entire category

# price: remove $, "Everyone", 

# content rating: ok

# genre: no changes

# last updated: convert to num 
# syntax: xxyyzz
# where xx month, yy day, zz year

# remove version

# remove android version

```

# Reviews df:
```{r}



```

# Exploratory Data Analysis


# Placeholder Section A


# Placeholder Section B


# Conclusion

